% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{\sc Jeffrey D. Michler}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, development, industrial organization},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}
  	{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{-.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
%{\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \name}

\vspace{0.25in}

\begin{minipage}{0.72\linewidth}
	\href{https://www.arizona.edu/}{University of Arizona} \\
	\href{https://economics.arizona.edu/}{Dept. of Agricultural and Applied Economics} \\
	McClelland Park 301K \\
	Tucson, AZ 85721  \\
	1.520.621.9809 \\
	
	
\end{minipage}
\begin{minipage}{0.28\linewidth}
	\begin{tabular}{r}
		\href{mailto:jdmichler@arizona.edu}{\tt jdmichler@arizona.edu} \\
		\href{https://economics.arizona.edu/person/jeffrey-d-michler}{\textcolor{Blue}{Departmental Website}} \\
		\href{https://aidelab.arizona.edu}{\textcolor{Blue}{AIDE Lab Website}} \\
		\href{https://orcid.org/0000-0001-7778-8703}{\textcolor{Blue}{ORCiD ID}} \\
		\href{https://github.com/jdavidm}{\textcolor{Blue}{Github}} \\
	\end{tabular}
\end{minipage}

\section*{\sc Academic Appointments}
\begin{tabular}{ll}
	2022-		& Associate Professor, Dept. of Agricultural and Applied Economics, University of Arizona	 \\
	2018-22		& Assistant Professor, Dept. of Agricultural and Applied Economics, University of Arizona	 \\
	2017-18		& Assistant Professor, Dept. of Agricultural and Resource Economics, University of Saskatchewan \\
	2015-17 	& Post-Doctoral Fellow, University of Illinois \& ICRISAT - Zimbabwe \\
\end{tabular}

\section*{\sc Editorial Appointments}
\begin{tabular}{ll}
2026-		& Associate Editor, \emph{American Journal of Agricultural Economics}	 \\
2024-		& Associate Editor, \emph{European Review of Agricultural Economics}	 \\
2023-		& Associate Editor, \emph{Agricultural Economics}	 \\
\end{tabular}


\section*{\sc Affiliations}
\begin{tabular}{ll}
2025- 		& Country Affiliate, Standing Panel on Impact Assessment (SPIA)	 \\
2020- 		& Catalyst, Berkeley Initiative for Transparency in the Social Sciences (BITSS)	 \\
2020-25     & Affiliate, Arizona Institute for Resilience in International Development (AIRID) \\
2020-25		& Affiliate, Humanitarian Assistance Technical Support (HATS) Initiative \\
2019-22		& Short-Term Consultant, World Bank \\
2018-23		& Adjunct Professor, Dept. of Agricultural and Resource Economics, University of Saskatchewan \\
\end{tabular}

\section*{\sc Education}
\begin{itemize}
	\item Ph.D. Agricultural Economics, Purdue University, May 2015
	\item M.A., Economics, New School for Social Research, December 2009
	\item M.A., Theology, \emph{magna cum laude}, St. Vladimir's Orthodox Theological Seminary, May 2007
	\item B.A., Economics and History, \emph{cum laude}, Bethel University, May 2003  
\end{itemize}

\section*{\sc Publications and Presentations \small (Citations: 2,325 \ \ \ h-Index: 18 \ \ \ i10-Index: 23)} 

\begin{itemize}
\item {\bf Books}
	
\leftskip 0.25in
\parindent -0.5in
\subitem Josephson, A. and J.D. Michler. 2024. \href{https://www.routledge.com/Research-Ethics-in-Applied-Economics-A-Practical-Guide/Josephson-Michler/p/book/9780367457419}{\emph{Research Ethics in Applied Economics: A Practical Guide}}. New York: Routledge. \\

\newpage
\leftskip 0in
\item {\bf Journal Articles}

\leftskip 0.25in
\parindent -0.5in
\subitem[26] Tjernstr\"{o}m, E., D. Ghanem, O. Barriga Cabanillas, T.J. Lybbert, A. Michuda, J.D. Michler. 2026. ``Comment on Suri (2011) `Selection and Comparative Advantage in Technology Adoption'.'' \emph{Econometrica}, conditional acceptance.
\subitem[25] Michler, J.D., D.A. Al Rafi, J. Giezendanner, A. Josephson, V. Pede, and E. Tellman. 2026 ``\href{https://doi.org/10.1016/j.jdeveco.2025.103648}{Impact Evaluations in Data-Scarce Environments: The Case of Stress-Tolerant Rice Varieties in Bangladesh}.'' \emph{Journal of :Development Economics 179}: 103648.
\subitem[24] Josephson, A., J.D. Michler, T. Kilic, and S. Murray. 2026. ``\href{https://doi.org/10.1016/j.jdeveco.2025.103553}{The Mismeasure of Weather: Using Earth Observation Data for Estimation of Socioeconomic Outcomes}.'' \emph{Journal of Development Economics 178}:  103553. Available as \href{http://documents.worldbank.org/curated/en/099850401072516334/IDU16cb26542195d814cc21b3191ae81d19d57ec}{World Bank Policy Research Working Paper No. 11015}.
\subitem[23] McCann, L.E., J.D. Michler, M. Mwangala, O. Olurotimi, and N. Estrada Carmona. 2025. `` \href{https://doi.org/10.1111/ajae.70026}{Food Without Fire: Nutritional and Environmental Impacts from a Solar Stove Field Experiment}.'' \emph{American Journal of Agricultural Economics}.
\subitem[22] Furbush, A., A. Josephson, T. Kilic, and J.D. Michler. 2025. ``\href{https://doi.org/10.1016/j.foodpol.2025.102819}{Coping or Hoping? Livelihood Diversification and Food Insecurity in the COVID-19 Pandemic}.'' \emph{Food Policy 131}: 102819. Available as \href{http://documents.worldbank.org/curated/en/099830101072519538/IDU1b45f8bf4104061493a18b9e12cfbee039761}{World Bank Policy Research Working Paper No. 11014}.
\subitem[21] Athnos, A., A. Josephson, J.D. Michler, and L. Rudin-Rush. 2025. ``\href{https://doi.org/10.71162/aetr.369516}{Expanding Undergraduate Research Experience: Opportunities, Challenges, and Lessons for the Future}.'' \emph{Applied Economics Teaching Resources 7} (2): 369516.
\subitem[20] Michler, J.D., A. Josephson, T. Kilic, and S. Murray. 2022. ``\href{https://doi.org/10.1016/j.jdeveco.2022.102927}{Privacy Protection, Measurement Error, and the Integration of Remote Sensing and Socioeconomic Survey Data}.'' \emph{Journal of Development Economics 158}: 102927.
\begin{itemize}
        \leftskip 0.25in
	\parindent -0.5in
	\item[\textbullet] 2022 AAEA International Section Best Publication - Honorable Mention
\end{itemize}
\subitem[19] Rudin-Rush, L., J.D. Michler, A. Josephson, and J.R. Bloem. 2022. ``\href{https://doi.org/10.1016/j.foodpol.2022.102306}{Food Insecurity During the First Year of the COVID-19 Pandemic in Four African Countries}.'' \emph{Food Policy 111}: 102306.
\subitem[18] Michler, J.D., F. Viens, and G. Shively. 2022. ``\href{https://doi.org/10.1002/jaa2.9}{Risk, Crop Yields, and  Weather Index Insurance in Village India}.'' \emph{Journal of the Agricultural \& Applied Economics Association 1} (1): 61-81. 
\subitem[17] Josephson, A., T. Kilic, and J.D. Michler. 2021. ``\href{https://www.nature.com/articles/s41562-021-01096-7}{Socioeconomic Impacts of COVID-19 in Low-Income Countries}.'' \emph{Nature Human Behaviour 5}: 557-65. Available as \href{https://openknowledge.worldbank.org/handle/10986/34733}{World Bank Policy Research Working Paper No. 9466}.
\subitem[16] Arouna, A., J.D. Michler, and J.C. Lokossou. 2021.  ``\href{https://doi.org/10.1016/j.jdeveco.2021.102626}{Contract Farming and Rural Transformation: Evidence from a Field Experiment in Benin}.'' \emph{Journal of Development Economics 151}: 102626. Available as \href{https://www.nber.org/papers/w25665.pdf}{NBER Working Paper No. 25665}.
\begin{itemize}
        \leftskip 0.25in
	\parindent -0.5in
	\item[\textbullet] 2022 AAEA Quality of Research Discovery Award
\end{itemize}
\subitem[15] Arouna, A., J.D. Michler, W.G. Yergo, and K. Saito. 2021. ``\href{https://doi.org/10.1111/ajae.12151}{One Size Fits All? Experimental Evidence on the Digital Delivery of Personalized Extension Advice in Nigeria}.'' \emph{American Journal of Agricultural Economics 103} (2): 596-619.
\begin{itemize}
        \leftskip 0.25in
        \parindent -0.5in
        \item[\textbullet] 2021 AAEA Africa Section Best Publication Award
\end{itemize}
\subitem[14] Michler, J.D., W. Masters, and A. Josephson. 2021. ``\href{https://doi.org/10.1002/aepp.13132}{Research Ethics Beyond the IRB: Selection Bias and the Direction of Innovation in Applied Economics}.'' \emph{Applied Economic Perspectives and Policy 43} (4): 1352-65.
\subitem[13] Janzen, S. and J.D. Michler. 2021. ``\href{https://doi.org/10.1002/aepp.13133}{Ulysses' Pact or Ulysses' Raft: Using Pre-Analysis Plans in Experimental and Nonexperimental Research}.'' \emph{Applied Economic Perspectives and Policy 43} (4): 1286-1304.
\subitem[12] Michler, J.D. and S.Y Wu. 2020. ``\href{https://doi.org/10.1016/j.jebo.2020.09.031}{Governance and Contract Choice: Theory and Evidence from Groundwater Irrigation Markets}.'' \emph{Journal of Economic Behavior \& Organization 180}: 129-47.
\subitem[11] Michler, J.D. 2020. ``\href{https://doi.org/10.1016/j.worlddev.2020.104888}{Agriculture in the Process of Development: A Micro-Perspective}.'' \emph{World Development 129}: 104888.
\subitem[10] Michler, J.D. and S.Y. Wu. 2020. ``\href{https://doi.org/10.1146/annurev-resource-101719-034514}{Relational Contracts in Agriculture: Theory and Evidence}.'' \emph{Annual Review of Resource Economics 12}: 111-27.
\subitem[9] Michler, J.D., E. Tjernstr\"{o}m, S. Verkaart, and K. Mausch. 2019. ``\href{https://doi.org/10.1093/ajae/aay050}{Money Matters: The Role of Yields and Profits in Agricultural Technology Adoption}.'' \emph{American Journal of Agricultural Economics 101} (3): 710-31.
\begin{itemize}
        \leftskip 0.25in
	\parindent -0.5in
	\item[\textbullet] 2019 \emph{American Journal of Agricultural Economics} Best Article Award
\end{itemize}
\subitem[8] Michler, J.D., K. Baylis, M. Arends-Kuenning, and K. Mazvimavi. 2019. ``\href{https://doi.org/10.1016/j.jeem.2018.11.008}{Conservation Agriculture and Climate Resilience}.'' \emph{Journal of Environmental Economics and Management 93}: 148-69. 
\subitem[7] Slade, P., J.D. Michler, and A. Josephson. 2019. ``\href{https://doi.org/10.1093/aepp/ppz010}{Foreign Geographical Indications, Consumer Preferences, and the Domestic Market for Cheese}.'' \emph{Applied Economic Perspectives and Policy 41} (3): 370-90. 
\subitem[6] Josephson, A. and J.D. Michler. 2018. ``\href{https://doi.org/10.1016/j.foodpol.2018.08.001}{Beasts of the Field? Ethics in Agricultural and Applied Economics}.'' \emph{Food Policy 79}: 1-11.
\subitem[5] Barriga Cabanillas, O., J.D. Michler, A. Michuda, and E. Tjernstr\"{o}m. 2018. ``\href{http://www.stata-journal.com/article.html?article=st0517}{Fitting and Interpreting Correlated Random-Coefficient Models Using Stata}.'' \emph{Stata Journal 18} (1): 159-73.
\subitem[4] Michler, J.D. and A. Josephson. 2017.  ``\href{https://doi.org/10.1016/j.worlddev.2016.08.011}{To Specialize or Diversify: Agricultural Diversity and Poverty Dynamics in Ethiopia}.'' \emph{World Development 89}: 214-26.
\subitem[3] Michler, J.D. and J.V. Balagtas. 2017. ``\href{https://doi.org/10.1111/agec.12320}{The Importance of the Savings Device in Precautionary Savings: Empirical Evidence from Rural Bangladesh}.'' \emph{Agricultural Economics 48} (2): 129-41.
\subitem[2] Verkaart, S., B. Munyua, K. Mausch, and J.D. Michler. 2017. ``\href{https://doi.org/10.1016/j.foodpol.2016.11.007}{Welfare Impacts of Improved Chickpea Adoption: A Pathway for Rural Development in Ethiopia?}''  \emph{Food Policy 66}: 50-61.
\subitem[1] Michler, J.D. and G. Shively. 2015. ``\href{https://doi.org/10.1111/1477-9552.12082}{Land Tenure, Tenure Security and Farm Efficiency: Panel Evidence from the Philippines}.'' \emph{Journal of Agricultural Economics 66} (1): 155-69. \\


\leftskip 0in
\item {\bf Book Chapters}

\leftskip 0.25in
\parindent -0.5in
\subitem Michler, J.D. and A. Josephson. 2022. ``\href{https://doi.org/10.4337/9781800372054.00019}{Recent Developments in Inference: Practicalities for the Applied Economist}.'' In J. Roosen and J.E. Hobbs, eds., \emph{A Modern Guide to Food Economics}. Cheltenham: Edward Elgar Publishing.
\subitem Furbush, A., A. Josephson, T. Kilic, and J.D. Michler. 2021. ``\href{https://voxeu.org/content/shaping-africa-s-post-covid-recovery}{The Evolving Impact of COVID-19 in Four African Countries},'' in R. Arezki, S. Djankov, and U. Panizza, eds., \emph{Shaping Africa’s Post-Covid Recovery}. London: CEPR Press. Available as \href{https://documents.worldbank.org/en/publication/documents-reports/documentdetail/810651614623398314/the-evolving-socioeconomic-impacts-of-covid-19-in-four-african-countries}{World Bank Policy Research Working Paper No. 9556}.  \\

\leftskip 0in
\item {\bf In Review}

\leftskip 0.25in
\parindent -0.5in
\subitem Benami, E., M. Cecil, A. Josephson, G. Maskell, and J.D. Michler. ``\href{http://arxiv.org/abs/2510.05108}{The Uses (and Misuses) of Weather and Earth Observation Data in Geospatial Impact Evaluations}.''
\subitem Michler, J.D., E. Benami,  A. Josephson, G. Maskell, M. Cecil, P. Behrer, R. Heilmayr, S. Gourlay, and K.Singh. ``Considerations and Resources for Integrating EO and Socioeconomic Data.''  \\


\leftskip 0in
\item {\bf In Preparation}

\leftskip 0.25in
\parindent -0.5in

\subitem Michler, J.D., K. Douglas, and A. Josephson. ``Mining Meaning: Conducting AI-Assisted Reviews of Economic Literature.''
\subitem Michler, J.D., A. Josephson, C.D. Agme and T. Kilic. ``Variable Selection in Socioeconomic Applications of Remotely Sensed Weather Data: Insights from the LSMS-ISA.''
\subitem Kee-Tui, E., A. Josephson, and J.D. Michler. ``Labor, Credit, and Markets: Evidence from the Philippines, 1971-2016.''
\subitem Braham, R., A. Josephson, and J.D. Michler. ``Risk and Rainfall: Specification Sensitivity in Estimating Smallholder Risk Preferences.''
\subitem Michler, J.D., P. Slade, and S.Y. Wu. ``Approximation in Complex Pricing Mechanisms.''
\subitem Deutschmann, J.W., J.D. Michler, and E. Tjernstr\"{o}m. ``Complex Pricing and Consumer Behavior: Evidence from a Lab Experiment.''
\subitem Michler, J.D., S.D. Yun, and B. Gramig. ``A Dynamic Model of Firm Location in Two-Dimensional Space.''
\subitem Josephson, A., J.D. Michler, and A. Orr. ``An Industrious Revolution? Changes in the Household Economy in Rural Bangladesh.''
\subitem Baylis, K., M. Mallory, J.D. Michler, and T. Songsermsawa. ``Effects of Credit and Market Access on Farm Gate Prices in India.'' \\

\leftskip 0in
\item {\bf Reports, Briefs, and Policy Papers}

\leftskip 0.25in
\parindent -0.5in
\subitem Michler, J.D., A. Josephson, T. Kilic, and S. Murray. ``Estimating the Impact of Weather on Agriculture.'' \href{https://openknowledge.worldbank.org/handle/10986/36643}{World Bank Policy Research Working Paper No. 9867}.
\subitem Josephson, A., E. Kee-Tui, J.D. Michler, and S. Perez. 2020. ``Dissemination and Adoption of Bundled Agronomic Practices.'' Cardon Working Paper Series No. 202002.
\subitem ``Assessing the Contributions of Conservation Agriculture to Building Resilience to Drought.'' 2016. Literature Review Report 6924-EL04. VUNA, Pretoria, South Africa.
\subitem ``\href{http://www.icrisat.org/wp-content/uploads/Impact-Brief1_Pigeonpea-in-northern-Tanxzania-04Jul16_final-for-web.pdf}{Assessment of the Impact of Improved Pigeonpea Development in Northern Tanzania}.'' 2016. Impact Brief No. 1 Patancheru 502 324, Telangana, India: ICRISAT.
\subitem ``\href{http://www.icrisat.org/wp-content/uploads/Impact-Brief2_Sorghum-Improvement-in-Mali-04Jul16_final-for-web.pdf}{An Economic Assessment of Sorghum Improvement in Mali}.'' 2016. Impact Brief No. 2 Patancheru 502 324, Telangana, India: ICRISAT.
\subitem ``\href{http://www.icrisat.org/wp-content/uploads/Impact-Brief3_Fertilizer-Microdosing-RD-Zimbabwe-04Jul16_final-for-web.pdf}{Impact of Fertilizer Microdosing Research and Development in Semi-Arid Zimbabwe}.''  2016. Impact Brief No. 3 Patancheru 502 324, Telangana, India: ICRISAT.
\subitem ``Economic Impacts of Groundnut Research and Development in Malawi: 1982-2013.'' 2016. Impact Brief No. 4 Patancheru 502 324, Telangana, India: ICRISAT.
\subitem ``Impact Assessment of Pearl Millet Hybrids on Production in Northwest India.''  2016. Impact Brief No. 5 Patancheru 502 324, Telangana, India: ICRISAT. \\
\\
\\
\leftskip 0in
\item {\bf Invited Seminars, Conference Presentations, and Workshops} \\
\\
\begin{tabular}{lp{.92\linewidth}}
	2025	& William \& Mary (Williamsburg, VA), Makerere University (Kampala, Uganda), Midwest International Economic Development Conference (Urbana, IL), University of Oklahoma (Norman, OK) Planned: AAEA Annual Meeting (Denver, CO) \\
	2024	& NIFA Agriculture Policy Scholars Conference (New Orleans, LA), Caribbean Institute for Meteorology and Hydrology Workshop (Bridgetown, Barbados), SPIA Fest 2024 (New Delhi, India), IAAE Triennial Meeting (New Delhi, India), Texas A\&M (College Station, TX)  \\
	2023	& University of Idaho (Moscow, ID), Midwest International Economic Development Conference (Houston, TX), AERE Research Seminar, University of Sydney (Sydney, Australia), Honors Student Guest Lecture, University of Sydney (Sydney, Australia), WEAI International Conference (Melbourne, Australia), BITSS Research Seminar (Berkeley, CA), AAEA Annual Meeting (Washington, D.C.),  AAAE Triennial Meeting (Durban, South Africa), International Rice Congress (Manila, Philippines), Arizona State University (Tempe, AZ)  \\
	2022	& Pacific Conference for Development Economics (San Francisco, CA), CSAE Conference (virtual), Midwest International Economic Development Conference (Minneapolis, MN), SGA Annual Meeting (Frick, Switzerland), $44^{th}$ BREAD Conference (Evanston, IL), Nordic Conference in Development Economics (Helsinki, Finland), IFAD22 International Conference (Rome, Italy), AAEA Annual Meeting (Anaheim, CA)  \\
	2021	& SPIA Webinar Series (virtual), Pre-Doctoral Research in Economics Workshop (virtual), Feed the Future Agrilinks Webinar Series (virtual), AAEA Annual Meeting (Austin, TX), IAAE Triennial Meeting (virtual), NIFA Agriculture Policy Scholars Conference (virtual)  \\
    2020	& World Bank Development Data Group Learning Series (virtual), AAEA Annual Meeting (virtual), NIFA Agriculture Policy Scholars Conference (virtual), Michigan State University (virtual). Accepted, conference canceled due to COIVD-19: CSAE Conference (Oxford, England), SIOE Annual Meeting (Cambridge, MA) \\
	2019	& AAEA invited session at ASSA (Atlanta, GA), NBER Transforming Rural Africa Conference (Cambridge, MA), CSAE Conference (Oxford, England), University of Arizona (Tucson, AZ), IRRI Workshop on Improving Impact Assessment, Monitoring, and Evaluation (Rome, Italy), SIOE Annual Meeting (Stockholm, Sweden), AAEA Annual Meeting (Atlanta, GA), Arizona State University (Mesa, AZ), University of Minnesota (St. Paul, MN)  \\
	2018	& CSAE Conference (Oxford, England), Midwest International Economic Development Conference (Minneapolis, MN), University of Wisconsin (Madison, WI), PIM Workshop on Rural Transformation in the $21^{st}$ Century (Vancouver, Canada), IAAE Triennial Meeting (Vancouver, Canada), AAEA Annual Meeting (Washington, D.C.), University of Copenhagen (Copenhagen, Denmark) International Rice Congress (Singapore) \\
	2017	& AEA Annual Meeting (Chicago, IL), CSAE Conference (Oxford, England), University of Arizona (Tucson, AZ), SPIA/IFPRI Invited Conference on Impacts of International Agricultural Research (Nairobi, Kenya), AAEA Annual Meeting (Chicago, IL), Workshop on Relational Contracts (Evanston, IL) \\
	2016 	& University of Saskatchewan (Saskatoon, Canada), IFPRI (Washington, D.C.), AAAE Triennial Meeting (Addis Ababa, Ethiopia), AAEA Annual Meeting (Boston, MA), African School of Economics (Cotonou, Benin), Africa Rice (Cotonou, Benin), 3ie Workshop on Agricultural Risk Mitigation (Nairobi, Kenya), Pan-African Grain Legume Conference (Livingstone, Zambia) \\	
	2015 	& Econometric Society World Congress (Montreal, Canada), SIOE Annual Meeting (Cambridge, MA), IAAE Triennial Meeting (Milan, Italy), AAEA Annual Meeting (San Francisco, CA), Midwest International Economic Development Conference (Madison, WI) \\
	2014 	& International Rice Congress (Bangkok, Thailand), AAEA Annual Meeting (Minneapolis, MN), Midwest International Economic Development Conference (Minneapolis, MN), IRRI (Los Banos, Philippines) \\\end{tabular}
   
\section*{} 
\begin{tabular}{lp{.92\linewidth}}
	2013	& AAEA Annual Meeting (Washington, D.C.), IRRI (Los Banos, Philippines) \\
	2012 	& AAEA Annual Meeting (Seattle, WA), Purdue Experimental Economics Seminar (West Lafayette, IN) \\
	\end{tabular}
\end{itemize}

\section*{\sc Teaching}
\begin{itemize}
	\item {\bf University of Arizona} \\
	\begin{tabular}{ll}
		AAE497A/597A	& Coding for Applied Economists (Spring 2026) \\
		AAE513/ECON513	& Consumer Economics and Price Analysis (Spring 2020, 21, 22, 23, 24, 25, 26) \\
		AAE360	& Poverty and Development of Nations (Spring 2019, 20, 21, 22, 23, 24, 25) \\
		AAE516/ECON516	& Microeconomics of Agricultural Development (Spring 2019) \\
	\end{tabular}
	\\
	\leftskip 0in
	\item {\bf University of Saskatchewan} \\
	\begin{tabular}{ll}
		AREC 272	& Introduction to Agricultural Economics (Spring 2018) \\
	\end{tabular}
\end{itemize}

\begin{itemize}
	\item {\bf Purdue University} \\
	\begin{tabular}{ll}
		AGEC 217	& Principles of Macroeconomics - Instructor (Summer 2012) \\
		AGEC 217	& Principles of Macroeconomics - TA (Fall, 2011; Spring 2012) \\
	\end{tabular}
	\\

	\leftskip 0in
	\item {\bf Workshops and Other Teaching} \\
	\begin{tabular}{lp{\linewidth}}
		IRRI (Los Ba\~{n}os, Philippines) & Workshop on Advanced Methods of Impact Assessment \\
		& (co-taught with Anna Josephson, December 2019)  \\
  		WorldFish (Penang, Malaysia) & Workshop on Advanced Methods of Impact Assessment \\
  		& (co-taught with Mary Arends-Kuenning and Kathy Baylis, May 2017) \\
		ICRAF (Nairobi, Kenya) & Workshop on Advanced Methods of Impact Assessment \\
		& (co-taught with  Mary Arends-Kuenning and Kathy Baylis, September 2015)  \\
	\end{tabular} \\

	\item {\bf Graduate Student Supervision}
	\begin{itemize}
		\item Reece Branham, MS 2025 (co-advisor), Research Associate, TANGO International
        \item Rodrigo Guerra Su, MS 2025 (committee member), PhD student Ag Econ, Texas A\&M
		\item Chandrakant Agme, MS 2024 (co-advisor), Pre-Doc Applied Economics, Cornell University 
		\item Dewan Al Rafi, MS 2023 (co-advisor), PhD student AAE, University of Georgia
		\item Lorin Rudin-Rush, MS 2023 (co-advisor), PhD student AAE, University of Wisconsin
		\item Ann Furbush, MS 2022 (advisor), Analyst, Cambridge Econometrics
		\item Charles Meisch, MS 2022 (co-advisor), Research Associate, TANGO International
		\item Laura McCann, MS 2021 (advisor), PhD student Public Policy, University of Arizona
		\item Emil Kee-Tui, MS 2021 (co-advisor), PhD student Applied Economics, Cornell University
		\item Emily Joiner, MS 2020 (committee member)
		\item Cheng Zhou, MS 2020 (committee member) \\
	\end{itemize}

	\leftskip 0in
	\item {\bf Undergraduate Student Supervision}
	\begin{itemize}
        \item Jocelyn Tijerina, BS 2027 (expected)
        \item Nelson Semidey, BS 2027 (expected)
        \item Tim Leavy, BS 2027 (expected)
        \item George Hyland, BS 2025
        \item Kieran Douglas, BS 2025, MS ARE, University of California - Davis
        \item Aurora Seekins, BA 2025, MA Economics, Boston University
		\item Samantha Wetherell, BS 2023, MS Sustainability and the Environment, University of Oxford
		\item Andrew Soderberg, BS 2023, MS AREC, University of Arizona
		\item Alison Conley, BS 2020, MA Economics, Boston University
		\item Brian McGreal, BS 2020, MS AREC, University of Arizona \\
	\end{itemize}

	\leftskip 0in
	\item {\bf Supervision of Undergraduate Research Interns in Data Analysis and Applied Economics}
	\begin{itemize}
		\item Ella Anderson, BS Environmental \& Water Resource Economics, 2026 (expected)
		\item Kieran Douglas, BA Economics, 2025
		\item Rebeca Fingkreuw, BA Applied Humanities \& Economics, 2024
		\item Shayan Khan, BA Economics, Math, \& Arabic, 2026 (expected)
		\item Caroline Klinck, BS Management Information Systems, 2024
		\item Bryce Smets, BS Business Economics, 2025
		\item Marlon Spain, BA Economics \& Philosophy, Politics, Economics, and Law, 2024
		\item Jacob Taylor, B.S. Environmental and Water Resource Economics \& Computer Science, 2026 (expected)
		\item Tatum Bingham, BS Agribusiness Economics \& Management, 2023
		\item Reece Branham, BS Business Economics \& BA French, 2023
		\item Maxine Cruz, BS Ecology \& Evolutionary Biology, 2023
		\item Rodridgo Guerra Su, BS Agribusiness Economics \& Management, 2023
		\item Chi Nguyen, BA Environmental Studies, 2023
		\item Hope Njuguna, BA Environmental Studies, 2024
		\item Andrew Soderberg, BS Environmental \& Water Resource Economics, 2023
		\item Jake Thomason, BS Information Science, 2022 \\
	\end{itemize}


	\leftskip 0in
	\item {\bf Visiting Scholar Supervision}
	\begin{itemize}
		\item Ahsan Ali Rehmani, PhD University of Faisalabad (2021-22)
	\end{itemize}
\end{itemize}

\section*{\sc Research Grants, Awards, and Fellowships}
\begin{itemize}
	
	\item {\bf External Grants (\$3,926,180)}
	
	\begin{tabular}{llccc}
		\multicolumn{2}{l}{Standing Panel on Impact Assessment (SPIA)}	& \$1,250,000 	& PI			& 2024-27 \\	
		& \multicolumn{4}{p{\linewidth}}{``The Dynamics of CGIAR Agricultural Innovations in Uganda''} \\
		&&&& \\ 
		\multicolumn{2}{l}{USDA NIFA Hispanic-Serving Institutions Education Grant}	& \$1,000,000 	& Co-I			& 2022-26 \\	
		& \multicolumn{4}{p{\linewidth}}{``Equitable Agriculture and Environmental Management''} \\
		&&&& \\
		\multicolumn{2}{l}{USAID Bureau of Humanitarian Assistance (BHA)}	& \$1,000,000 	& Co-I			& 2022-25 \\	
		& \multicolumn{4}{p{\linewidth}}{``Enhancing Evidence for Humanitarian Action in the Face of Climate Change''} \\
		&&&& \\
		\multicolumn{2}{l}{World Bank Research Support Budget}	& \$95,000 	& PI			& 2021-22 \\	
		& \multicolumn{4}{p{\linewidth}}{``Understanding Households’ Resilience to and Recovery from COVID-19 in Sub-Saharan Africa''} \\
		&&&& \\
		\multicolumn{2}{l}{Berkeley Initiative for Transparency in the Social Sciences (BITSS)}	& \$1,680 	& Co-PI			& 2020-21 \\	
		& \multicolumn{4}{p{\linewidth}}{``Transparency, Replicability, \& Reproducibility in Agricultural and Applied Economics''} \\
        		&&&& \\
		\multicolumn{2}{l}{Standing Panel on Impact Assessment (SPIA)}	& \$300,000 	& PI			& 2020-23 \\	
		& \multicolumn{4}{p{\linewidth}}{``Evaluating the Impact of Stress-Tolerant Rice Varieties Through Remote Sensing and Econometric Methods''} \\
	\end{tabular}

	\begin{tabular}{llccc}
		\multicolumn{2}{l}{Standing Panel on Impact Assessment (SPIA)}	& \$42,000	& Co-PI			& 2017 \\	
		& \multicolumn{4}{p{\linewidth}}{``Workshop and Institutional Support for Advanced Methods in Impact Assessment''} \\
		&&&& \\
		\multicolumn{2}{l}{Strengthening Impact Assessment in the CGIAR (SIAC)}	& \$150,000	& Co-PI			& 2016-17 \\
		& \multicolumn{4}{p{\linewidth}}{``Documenting Adoption of Natural Resource Management (NRM) Practices: Evidence on Microdosing and Conservation Agriculture in Zimbabwe and Niger''} \\
		&&&& \\
		\multicolumn{2}{l}{U.S. Borlaug Fellowship in Global Food Security}	& \$15,000	& Fellowship	& 2012-13 \\
		& \multicolumn{4}{p{\linewidth}}{``Household Grain Storage and Food Security in Rural Bangladesh''} \\
	\end{tabular}
    \\	
	\leftskip 0in
	\item {\bf Internal Grants (\$165,500)} 

	\begin{tabular}{llccc}
		\multicolumn{5}{p{\linewidth}}{\sc University of Arizona} \\
		&\multicolumn{1}{l}{One Health Research Initiative}	& \$50,000 	& PI			& 2024-25 \\	
		&\multicolumn{1}{l}{AIRES RISE Initiative24}	& \$58,000 	& co-PI			& 2022-23 \\	
		&\multicolumn{1}{l}{Environment \& Resilience Vertically Integrated Projects (VIP)}	& \$4,000 	& 			& 2022 \\
        &\multicolumn{1}{l}{Economics Science Laboratory Seed Grant}	& \$1,000 	& PI			& 2022 \\	
		&\multicolumn{1}{l}{Arizona Institutes for Resilience (AIR) Seed Grant}	& \$7,500 	& co-PI			& 2021 \\	
	\end{tabular}
    
	\begin{tabular}{llccc}
		&\multicolumn{1}{l}{CALS Early Career Seed Grant}	& \$10,000 	& PI			& 2018-19 \\	
		\multicolumn{5}{p{\linewidth}}{\sc University of Saskatchewan} \\
		&\multicolumn{1}{l}{Global Ambassador Program Award}	& Can\$5,000	& 			& 2018-19 \\	
		&\multicolumn{1}{l}{President's SSHRC Research Fund}	& Can\$7,000	& PI			& 2017-18 \\	
		\multicolumn{5}{p{\linewidth}}{\sc University of Illinois at Urbana-Champaign} \\
		&\multicolumn{1}{l}{ACES International Joint Research Program Grant}	& \$20,000	& Co-PI			& 2016 \\
		\multicolumn{5}{p{\linewidth}}{\sc Purdue University} \\
		&\multicolumn{1}{l}{Climate Change Research Center Travel Grant}	& \$2,000	& 			& 2015 \\
		&\multicolumn{1}{l}{D. Thomas Woods Memorial Fund for International Studies}	& \$1,000	& 			& 2013 \\
	\end{tabular}
	
	\leftskip 0in
	\item {\bf Awards and Fellowships} \\
    \\
	\begin{tabular}{l}
		AAEA Outstanding Master's Thesis Award, advisor (with Anna Josephson), awarded to \\
		\hspace{0.1cm} Chandrakant Agme, 2025 \\
		Outstanding \emph{American Journal of Agricultural Economics} Reviewer Award, 2025 \\
		AAEA International Section Best Publication - Honorable Mention (with Anna Josephson, Talip  \\
		\hspace{0.1cm} Kilic, and Siobhan Murray), 2022 \\
		AAEA Quality of Research Discovery Award (with Aminou Arouna and Jourdain Lokossou), 2022 \\
		AAEA Outstanding Master's Thesis Award, advisor (with Anna Josephson), awarded to Emil \\
		\hspace{0.1cm} Kee-Tui, 2022 \\
		AAEA Africa Section Best Publication Award (with Aminou Arouna, Wilfried Yergo, and Kazuki \\
		\hspace{0.1cm} Saito), 2021 \\
		\emph{American Journal of Agricultural Economics} Best Article Award (with Emilia Tjernstr\"{o}m,
		Simone  \\
		\hspace{0.1cm} Verkaart, and Kai Mausch), 2019 \\
		\emph{World Bank Economic Review} Excellence in Refereeing Award, 2018 \\
		Best Dissertation,  Dept. of Agricultural Economics, Purdue, 2015 \\
		Young Rice Scientist Award, International Rice Congress, 2014 \\
		Frederick N. Andrews Fellowship, 2010-2012 \\
	\end{tabular}

\end{itemize}

\section*{\sc Professional and Academic Experience}
\begin{tabular}{ll}
	2019-22 & Short-Term Consultant, World Bank \\
	2013-15	& Graduate Research Assistant, Purdue University \\
	2013 	& Visiting Scholar, IRRI, Dhaka, Bangladesh \\
	2007-08 & Natural Resource Analyst, O\&M Partners, New York, NY \\
	2003-04 & High school teacher (economics and history), Hinkson Academy, Moscow \\
\end{tabular}

\section*{\sc Professional Service}
\begin{itemize}
\item \textbf{Journal reviewer} for \emph{African Journal of Agricultural and Resource Economics}, \emph{Agricultural Economics}, \emph{Agricultural Systems}, \emph{American Journal of Agricultural Economics}, \emph{Applied Economic Perspectives and Policy}, \emph{Australian Journal of Agricultural and Resource Economics}, \emph{Climate Change}, \emph{European Review of Agricultural Economics}, \emph{Food Policy}, \emph{Global Food Security}, \emph{Journal of African Economies}, \emph{Journal of the Agricultural and Applied Economics Association}, \emph{Journal of Agricultural Economics}, \emph{Journal of Agricultural and Food Research}, \emph{Journal of the Association of Environmental and Resource Economists}, \emph{Journal of Development Economics}, \emph{Journal of Development Studies}, \emph{Journal of Environment and Development}, \emph{Journal of Environmental Economics and Management}, \emph{Land Economics}, \emph{Land Use Policy}, \emph{Nature Human Behaviour}, \emph{PLOS ONE}, \emph{Resource Policy}, \emph{Review of Economics of the Household}, \emph{Review of Economics and Statistics}, \emph{World Bank Economic Review}, \emph{World Development}, \emph{World Development Perspectives}
\item \textbf{Member} of American Economic Association (AEA); Society for Institutional \& Organizational Economics (SIOE); Agricultural \& Applied Economics Association (AAEA); International Association of Agricultural Economists (IAAE); African Association of Agricultural Economists (AAAE)
\end{itemize}

\subsection*{Service to the Agricultural and Applied Economics Association (AAEA)}
\begin{itemize}
\item \textbf{Chair} Experimental Economics (EXECON) Section of the AAEA (2021-22), Chair-Elect (2020-21), Past-Chair (2022-23)
\item \textbf{Chair} of AAEA Quality of Research Discovery Award committee (2025)
\item \textbf{Member} of AAEA Quality of Research Discovery Award committee (2023-25)
\item \textbf{Chair} of AAEA EXECON Section Best Paper Award committee (2023)
\item \textbf{Member} of AAEA Outstanding Master's Thesis Award committee (2025-27)
\item \textbf{Co-Topic Leader}, experimental economics, AAEA annual meeting (2023, 2024)
\item \textbf{Abstract reviewer} for AAEA annual meeting (2015-23)
\end{itemize}

\subsection*{Service to Other Professional Organizations}
\begin{itemize}
\item \textbf{Abstract reviewer} for AAAE (2016, 2019, 2023); ICAE (2015, 2018, 2021, 2024); WAEA (2022); topic leader for WAEA (2020)
\item \textbf{Grant reviewer} for National Science Foundation (NSF); National Institute of Food and Agriculture (NIFA); International Initiative for Impact Evaluation (3ie)
\item \textbf{Book reviewer} for International Food Policy Research Center (IFPRI)
\end{itemize}

\subsection*{Service to the College and University}

\begin{itemize}
\item \textbf{Member}, Dean's Research Advisory Council (DRAC) (2025-26)
\item \textbf{Member}, Strategic Planning and Budget Advisory Committee (SPBAC) (2024-25)
\item \textbf{Member}, Advisory Council, Arizona Institutes for Resilience (AIR) International Programs (2021-23)
\textbf{Member}, University Fellows Selection Review Committees (2023)
\item \textbf{Department representative}, CALS Faculty Council, University of Arizona (2019); Graduate Student Advisory Council, College of Agriculture, Purdue University (2013-14)
\end{itemize}

\subsection*{Service to the Department}
\begin{itemize}
\item \textbf{Chair}, Undergraduate Curriculum Review Committee (2025)
\item \textbf{Chair}, AREC Behavioral Economics Hiring Committee (2023); AREC Environmental Economics Hiring Committee (2023)
\item \textbf{Chair}, AREC Website and Communication Committee (2018-24)
\item \textbf{Member}, AREC Research Professor Hiring Committee (2023); AREC Professor of Practice Hiring Committee (2021)
\item \textbf{Academic chair}, Graduate Student Organization, Purdue University (2013-14)
\end{itemize}


%\section*{\sc References}

%\begin{tabular}{llll}
%	Steven Wu & & & Kathy Baylis \\
%	Professor	& & & Professor \\
%	Department of Agricultural Economics	& & & Department of Geography \\
%	Purdue University & & & University of California, Santa Barbara \\
%	sywu@purdue.edu & & & baylis@ucsb.edu \\
%	 & & &  \\
%	 & & &  \\
%	Travis Lybbert & & &  \\
%	Professor	& & &  \\
%	Department of Agricultural \& Resource Economics	& & &  \\
%	University of California, Davis & & &  \\
%	tlybbert@ucdavis.edu & & &  \\
%\end{tabular}

\bigskip

% Footer
\begin{center}
	\begin{footnotesize}
		Last updated: \today \\
	\end{footnotesize}
\end{center}

\end{document}
